---
title: "PCI Reports"
format:
  docx:
    toc: true
    number-sections: true
    highlight-style: github
editor: visual
execute: 
  echo: false
---

```{r Data download, include=FALSE}
#Setup Temporary Directory for file storage
temp <- tempdir()
#Load in the helper functions/data required
source("HelperFunctions.R")
#Set data source type Powerbi or Sharepoint
data_source <- "Powerbi"

if(data_source == "Sharepoint"){
  #Sharepoint Token
tk_sp <- qiverse.azure::get_az_tk('sp')
#Load data from CSV
fsh_data <- qiverse.sharepoint::download_sharepoint_file(
  site_url = 'https://wahealthdept.sharepoint.com/sites/WACardiacOutcomeRegistry',
  file_url = 'https://wahealthdept.sharepoint.com/:x:/r/sites/WACardiacOutcomeRegistry/PCI/PCI%20Data/Latest%20NCR%20Submission/Fiona_Stanley_Hospital_2024_PCI_Data.csv?d=w502a1115d07d84e37976119fd0e5ed4e4&csf=1&web=1&e=CipGly',
  token = tk_sp)
rph_data <- qiverse.sharepoint::download_sharepoint_file(
  site_url = 'https://wahealthdept.sharepoint.com/sites/WACardiacOutcomeRegistry',
  file_url = 'https://wahealthdept.sharepoint.com/:x:/r/sites/WACardiacOutcomeRegistry/PCI/PCI%20Data/Latest%20NCR%20Submission/Royal_Perth_Hospital_2024_PCI_Data.csv?d=w7b047d9021874a58bd3241d2ad4837ef&csf=1&web=1&e=HXmpC4',
  token = tk_sp)
scgh_data <- qiverse.sharepoint::download_sharepoint_file(
  site_url = 'https://wahealthdept.sharepoint.com/sites/WACardiacOutcomeRegistry',
  file_url = 'https://wahealthdept.sharepoint.com/:x:/r/sites/WACardiacOutcomeRegistry/PCI/PCI%20Data/Latest%20NCR%20Submission/Sir_Charles_Gairdner_Hospital_2024_PCI_Data.csv?d=w970e2c01ddec4e8aa6456876e8c793b5&csf=1&web=1&e=Jc7bIW',
  token = tk_sp)

#Read in data from CSV
pci_data <- readr::read_csv(c(fsh_data, rph_data, scgh_data), col_types = colTypes)
} else if(data_source == "Powerbi"){
#PowerBI Token
tk = qiverse.azure::get_az_tk('pbi_df')
#Load data from PowerBI
data <- qiverse.powerbi::download_dataflow_table(workspace_name = "PCI Data Set",
                                              dataflow_name = "NCR Template and Hid files",
                                              table_name = "required_columns",
                                              access_token = tk$credentials$access_token)
#Workaround for setting csv col types
readr::write_csv(data, paste0(temp, ".csv"))
#Read in data from PowerBI
pci_data <- readr::read_csv(paste0(temp, ".csv"), col_types = colTypes)
}

```

```{r Data transformation, include=FALSE}
#Creating period start and end, first and last date of the month
pci_data <- pci_data |> 
  dplyr::mutate(period_start = lubridate::floor_date(dop, unit = "month"),
                period_end = lubridate::ceiling_date(period_start, unit = "month")-1)


#Creating required columns for Indicator calculations
pci_data <- pci_data |>
  dplyr::mutate(
    #Create dbd based on whether the tbd time occurred before/after top time
    dbd = dplyr::case_when(
      tbd <= top ~ dop + lubridate::days(1),
      tbd > top ~ dop, 
      tbd = NA ~ NA),
    #Calculate column required for ECG to PCI time
    ecgdb = difftime(tbd, tecgd, units = "mins") + difftime(dbd, decgd, units = "mins"),
    #Calculate column required for Door to PCI time
    dbdt = difftime(tbd, toa, units = "mins") + difftime(dbd, doa, units = "mins"))
```

```{r Indicator Definitions, include=FALSE}
#Time from diagnostic ECG to PCI mediated reperfusion
pci_data <- pci_data |>
  dplyr::mutate(NCR1_den = dplyr::if_else(pci == "1" &
                ecgdb >= 0 &
                ecgdb <= 500, 1, 0))

#Time from door to PCI mediated reperfusion
pci_data <- pci_data |>
  dplyr::mutate(NCR2_den = dplyr::if_else(pci == "1" &
                dbdt >= 0 &
                dbdt <= 500, 1, 0))

#Peri-PCI stroke
pci_data <- pci_data |>
dplyr::mutate(NCR3_den = dplyr::if_else(ihstr != "",1,0))

#In-hospital major bleeding
pci_data <- pci_data |> 
  dplyr::mutate(NCR4_den = dplyr::if_else(is.na(ihbl) == F, 1, 0, missing = 0),
                NCR4_num = dplyr::if_else(NCR4_den == 1 &
                                          stringr::str_detect(ihbl, "[2345678]"), 1, 0, missing = 0))

#In-hospital mortality
pci_data <- pci_data |>
  dplyr::mutate(NCR5_den = 1,
                NCR5_num = ifelse(dis == "6", 1, 0))

#30 day unplanned cardiac readmission rate after PCI
pci_data <- pci_data |>
  dplyr:::mutate(NCR6_den = ifelse(dis != "6", 1, 0),
                 NCR6_num = ifelse(NCR6_den == 1 &
                              crh30 == "1" &
                              pc30 != "1", 1, 0))

#Unplanned revascularisation within 30 days
pci_data <- pci_data |> 
  dplyr::mutate(NCR7_den = 1,
                NCR7_num = dplyr::if_else((ihpci == 1 &
                                          ihpcip == 0 &
                                          ihtvr == 1) |
                                          (ihcab == 1 &
                                          ihpcab == 0 &
                                          ihtvcab == 1) |
                                          (crh30 == 1 &
                                          pc30 == 0 &
                                          (tvr30 == 1 | tvcab30 == 1)), 1, 0, missing = 0))

#30 day mortality after PCI
pci_data <- pci_data |> 
  dplyr::mutate(NCR8_den = 1,
                NCR8_num = dplyr::if_else((dop + 30) <= dmort30 |
                                          dis == "6", 1, 0, missing = 0))

#Patients without contraindication discharged on lipid-lowering therapy
pci_data <- pci_data |> 
  dplyr::mutate(NCR9_den = dplyr::if_else(dis != "6" & 
                                          dstp != "2" & 
                                          doll != "2" & 
                                          is.na(dstp) == F &
                                          is.na(doll) == F &
                                          dstp != "3" & 
                                          doll != "3" & 
                                          dstp != "" & 
                                          doll != "", 1, 0, missing = 0),
                NCR9_num = dplyr::if_else(NCR9_den == 1 & 
                                         (dstp == "1" | doll == "1"), 1, 0, missing = 0))

#Patients referred to cardiac rehabilitation or other secondary prevention program
pci_data <- pci_data |> 
  dplyr::mutate(NCR10_den = dplyr::if_else(dis != "6" &
                                           crehab != "-1" &
                                           crehab != "", 1, 0, missing = 0),
                NCR10_num = dplyr::if_else(NCR10_den == 1 & 
                                           crehab == "1", 1, 0, missing = 0))

#Proportion of patients without a clear and documented contraindication for aspirin and/or a P2Y12 inhibitor, discharged on DAPT
pci_data <- pci_data |> 
  dplyr::mutate(NCR11_den = dplyr::if_else(dis != "6" & 
                                           dasp != "2" & 
                                           doap != "2" & 
                                           is.na(dasp) == F &
                                           is.na(doap) == F &
                                           dasp != "3" & 
                                           doap != "3" & 
                                           dasp != "" & 
                                           doap != "", 1, 0, missing = 0),
                NCR11_num = dplyr::if_else(NCR11_den == 1 & 
                                          (dasp == "1" | doap == "1"), 1, 0, missing = 0))
```

## Time from diagnostic ECG to PCI mediated reperfusion

### SPC

```{r NCR1 SPC}
## Generate the SPC chart
NCR1_spc <- controlcharts::spc(data = dplyr::filter(pci_data, NCR1_den == 1),
                   keys = period_end,
                   numerators = ecgdb,
                   aggregations = list(numerators = "median"),
                   spc_settings = list(chart_type = "i"),
                   y_axis_settings = list(ylimit_label = "Median time from ECG to PCI (Minutes)",
                                          ylimit_sig_figs = 0,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR1_spc
```

## Time from door to PCI mediated reperfusion

### SPC

```{r NCR2 SPC}
## Generate the SPC chart
NCR2_spc <- controlcharts::spc(data = dplyr::filter(pci_data, NCR2_den == 1),
                   keys = period_end,
                   numerators = dbdt,
                   aggregations = list(numerators = "median"),
                   spc_settings = list(chart_type = "i"),
                   y_axis_settings = list(ylimit_label = "Median time from door to PCI (Minutes)",
                                          ylimit_sig_figs = 0,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR2_spc
```

## Peri-PCI stroke

### Funnel

```{r NCR3 Funnel}
## Generate the Funnel chart
NCR3_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = ihstr,
                      denominators = NCR3_den,
                      y_axis_settings = list(ylimit_u = 2,
                                             ylimit_label = "Percentage of in-hospital stroke after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR3_fpl$static_plot
```

The funnel plot above displays the information for **Peri-PCI Stroke** between **`r min(pci_data$period_start)`** and **`r max(pci_data$period_end)`**. The mean (or center line) value statewide is **`r round(NCR3_fpl$limits$target[1], 2)`**.

```{r NCR3 SPC}
## Generate the SPC chart
NCR3_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = ihstr,
                   denominators = NCR3_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "Percentage of in-hospital stroke after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR3_spc
```

The Statistical Process Control (SPC) chart above displays the information for **Peri-PCI Stroke** between **`r min(pci_data$period_start)`** and **`r max(pci_data$period_end)`**. There was a total numerator of **`r format(sum(unlist(do.call(rbind,NCR3_fpl$html_plot$x$data_raw)[,3])), scientific = F, big.mark = ",")`**. There was a total denominator of **`r format(sum(unlist(do.call(rbind,NCR3_fpl$html_plot$x$data_raw)[,4])), scientific = F, big.mark = ",")`**. The mean (or center line) value statewide is **`r round(NCR3_fpl$limits$target[1], 2)`**.

## In-Hospital Major Bleeding

### Funnel

```{r NCR4 Funnel}
## Generate the Funnel chart
NCR4_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR4_num,
                      denominators = NCR4_den,
                      y_axis_settings = list(ylimit_u = 2,
                                             ylimit_label = "Percentage of in-hospital major bleeding after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR4_fpl
```

### SPC

```{r NCR4 SPC}
## Generate the SPC chart
NCR4_spc <- controlcharts::spc(data = dplyr::filter(pci_data, NCR4_den > 0),
                   keys = period_end,
                   numerators = NCR4_num,
                   denominators = NCR4_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "Percentage of in-hospital major bleeding after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR4_spc
```

## In-hospital mortality

### Funnel

```{r NCR5 Funnel}
## Generate the Funnel chart 
NCR5_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR5_num,
                      denominators = NCR5_den,
                      y_axis_settings = list(ylimit_u = 5,
                                             ylimit_label = "Percentage of in-hospital mortality after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR5_fpl
```

### SPC

```{r NCR5 SPC}
## Generate the SPC chart 
NCR5_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR5_num,
                   denominators = NCR5_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "Percentage of in-hospital mortality after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR5_spc
```

## 30 day unplanned cardiac readmission rate after PCI

Cardiac readmission data is currently undergoing review. This data was not included in the 2024 NCR data submission.

### Funnel

```{r NCR6 Funnel}
## Generate the Funnel chart
NCR6_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR6_num,
                      denominators = NCR6_den,
                      y_axis_settings = list(ylimit_u = 10,
                                             ylimit_label = "Percentage of 30 day unplanned cardiac readmissions after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR6_fpl
```

### SPC

```{r NCR6 SPC}
## Generate the SPC chart 
NCR6_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR6_num,
                   denominators = NCR6_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "Percentage of 30 day unplanned cardiac readmissions after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR6_spc
```

## 30 day unplanned revascularisation rate after PCI

### Funnel

```{r NCR7 Funnel}
## Generate the Funnel chart
NCR7_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR7_num,
                      denominators = NCR7_den,
                      y_axis_settings = list(ylimit_label = "Percentage of 30 day unplanned revascularisation after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR7_fpl
```

### SPC

```{r NCR7 SPC}
## Generate the SPC chart
NCR7_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR7_num,
                   denominators = NCR7_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "Percentage of 30 day unplanned revascularisation after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR7_spc
```

## 30 Day Mortality

### Funnel

```{r NCR8 Funnel}
## Generate the Funnel chart
NCR8_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR8_num,
                      denominators = NCR8_den,
                      y_axis_settings = list(ylimit_u = 5,
                                             ylimit_label = "Percentage of 30 day mortality after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR8_fpl
```

### SPC

```{r NCR8 SPC}
## Generate the SPC chart
NCR8_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR8_num,
                   denominators = NCR8_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "Percentage of 30 day mortality after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR8_spc
```

## Patients Referred to Cardiac Rehabilitation

### Funnel

```{r NCR10 Funnel}
## Generate the Funnel chart
NCR10_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR10_num,
                      denominators = NCR10_den,
                      y_axis_settings = list(ylimit_l = 70,
                                             ylimit_label = "Percentage of patients referred to cardiac rehab after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "increase",
                                              three_sigma = TRUE))
NCR10_fpl
```

### SPC

```{r NCR10 SPC}
## Generate the SPC chart 
NCR10_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR10_num,
                   denominators = NCR10_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "Percentage of patients referred to cardiac rehab after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "increase",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR10_spc
```

## Patients Discharged on Lipid-Lowering Therapy

### Funnel

```{r NCR9 Funnel}
## Generate the Funnel chart
NCR9_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR9_num,
                      denominators = NCR9_den,
                      y_axis_settings = list(ylimit_u = 100,
                                             ylimit_l = 95,
                                             ylimit_label = "Percentage of patients discharged on Lipid Lowering Therapy after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "increase",
                                              three_sigma = TRUE))
NCR9_fpl
```

### SPC

There is an explained error in the discharge medication data for October 2021, this point can be ignored for analysis.
```{r NCR9 SPC}
## Generate the SPC chart 
NCR9_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR9_num,
                   denominators = NCR9_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "Percentage of patients discharged on Lipid Lowering Therapy after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "increase",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR9_spc
```

## Patients Discharged on Dual Antiplatelet Therapy

### Funnel

```{r NCR11 Funnel}
## Generate the Funnel chart
NCR11_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR11_num,
                      denominators = NCR11_den,
                      y_axis_settings = list(ylimit_u = 100,
                                             ylimit_l = 95,
                                             ylimit_label = "Percentage of patients discharged on Dual Antiplatelet Therapy after PCI",
                                             ylimit_sig_figs = 0,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "increase",
                                              three_sigma = TRUE))
NCR11_fpl
```

### SPC

There is an explained error in the discharge medication data for October 2021, this point can be ignored for analysis.
```{r NCR11 SPC}
## Generate the SPC chart 
NCR11_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR11_num,
                   denominators = NCR11_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "Percentage of patients discharged on Dual Antiplatelet Therapy after PCI",
                                          ylimit_sig_figs = 0,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "increase",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR11_spc
```
