---
title: "Percutaneous Coronary Interventions Report"
format:
  docx:
    toc: true
    number-sections: true
    highlight-style: github
    fig-format: svg
execute:
  echo: false
---

```{r Data download, include=FALSE}
if (!file.exists("./pci_data.csv")) {
  stop("NCR dataset not found! Please check that you have a single CSV file named 'pci_data.csv' in the current directory!",
       call. = FALSE)
}

#Load in the helper functions/data required
source("HelperFunctions.R")

#Read in data from PowerBI
pci_data <- readr::read_csv("./pci_data.csv", col_types = colTypes)
```

```{r Data transformation, include=FALSE}
#Creating period start and end, first and last date of the month
pci_data <- pci_data |>
  dplyr::mutate(period_start = lubridate::floor_date(dop, unit = "month"),
                period_end = lubridate::ceiling_date(period_start, unit = "month")-1)

# Creating variables for demographics
pci_data <- pci_data |>
  dplyr::mutate(
    # Calculate BMI variable
    bmi = wkg/(htm/100)^2,
    # Assign text or category labels to demographic columns
    # Sex
    sex_name = factor(sex, levels = c(1, 2), labels = c("Male", "Female")),
    # Age
    age_cat = dplyr::case_when(
      age <= 40 ~ "<= 40 yrs",
      age >= 41 & age <= 50 ~ "41-50 yrs",
      age >= 51 & age <= 60 ~ "51-60 yrs",
      age >= 61 & age <= 70 ~ "61-70 yrs",
      age >= 71 & age <= 80 ~ "71-80 yrs",
      age > 80 ~ ">= 81 yrs"
    ),
    # Set as factor so that label ordering will be respected
    age_cat = factor(age_cat, levels = c("<= 40 yrs", "41-50 yrs", "51-60 yrs",
                                         "61-70 yrs", "71-80 yrs", ">= 81 yrs")),
    inds_cat = factor(inds, levels = c(0, 1, 2, 3, -1), labels =  c("Neither", "Aboriginal",
                                                                    "Torres Strait Islander", "Both",
                                                                   "Unknown")),
    # Aboriginality
    inds_name = dplyr::case_when(
      inds == 0 ~ "Not Aboriginal",
      inds %in% c(1, 2, 3) ~ "Aboriginal",
      inds == -1 ~ "Unknown"
    )
  )

#Creating required columns for Indicator calculations
pci_data <- pci_data |>
  dplyr::mutate(
    #Create dbd based on whether the tbd time occurred before/after top time
    dbd = dplyr::case_when(
      tbd <= top ~ dop + lubridate::days(1),
      tbd > top ~ dop,
      tbd = NA ~ NA),
    #Calculate column required for ECG to PCI time
    ecgdb = difftime(tbd, tecgd, units = "mins") + difftime(dbd, decgd, units = "mins"),
    #Calculate column required for Door to PCI time
    dbdt = difftime(tbd, toa, units = "mins") + difftime(dbd, doa, units = "mins"),
    #Calculate column required for Symptoms to Door time
    symptom_to_door = difftime(toa, tso, units = "mins") + difftime(doa, dso, units = "mins"),
    #Calculate if patient was an inpatient at time of ACS
    inp = dplyr::case_when(
      acs == "1" & symptom_to_door > 0 ~ "0",
      acs == "1" & symptom_to_door <= 0 ~ "1",
      acs == "0" ~ NA))
```

```{r Indicator Definitions, include=FALSE}
#Time from diagnostic ECG to PCI mediated reperfusion
pci_data <- pci_data |>
  dplyr::mutate(NCR1_den = dplyr::if_else(pci == "1" &
                inp == "0" &
                iht == "0" &
                ecgdb > 0 &
                symptom_to_door < 720, 1, 0))

#Time from door to PCI mediated reperfusion
pci_data <- pci_data |>
  dplyr::mutate(NCR2_den = dplyr::if_else(pci == "1" &
                inp == "0" &
                iht == "0" &
                dbdt > 0 &
                symptom_to_door < 720, 1, 0))

#Peri-PCI stroke
pci_data <- pci_data |>
dplyr::mutate(NCR3_den = dplyr::if_else(ihstr == 0 | ihstr == 1, 1,0))

#In-hospital major bleeding
pci_data <- pci_data |>
  dplyr::mutate(NCR4_den = dplyr::if_else(stringr::str_detect(ihbl, "[012345678]"), 1, 0, missing = 0),
                NCR4_num = dplyr::if_else(NCR4_den == 1 &
                                          stringr::str_detect(ihbl, "[34578]"), 1, 0, missing = 0))

#In-hospital mortality
pci_data <- pci_data |>
  dplyr::mutate(NCR5_den = dplyr::if_else(stringr::str_detect(dis, "[123456]"), 1, 0, missing = 0),
                NCR5_num = dplyr::if_else(dis == "6", 1, 0))

#30 day unplanned cardiac readmission rate after PCI
pci_data <- pci_data |>
  dplyr::mutate(NCR6_den = dplyr::if_else(
      stringr::str_detect(dis, "[12345]") &
      (stat30 == "1" | stat30 == "0") &
      (crh30 == "1"  | crh30 == "0"), 1, 0),
                NCR6_num = dplyr::if_else(NCR6_den == 1 &
                              crh30 == "1" &
                              pc30 == "0", 1, 0))

#Unplanned revascularisation within 30 days
pci_data <- pci_data |>
  dplyr::mutate(NCR7_den = dplyr::if_else(
    (ihpci == "0" | ihpci == "1") &
    (ihcab == "0" | ihcab == "1"), 1, 0, missing = 0),
                NCR7_num = dplyr::if_else(NCR7_den == 1 &
                  (ihpci == "1" & ihpcip == "0") |
                  (ihcab == "1" & ihpcab == "0" & ihtvcab == "1") |
                  (pc30 == "0" & pci30 == "1") |
                  (pc30 == "0" & cab30 == "1"), 1, 0, missing = 0))

#30 day mortality after PCI
pci_data <- pci_data |>
  dplyr::mutate(NCR8_den = dplyr::if_else(
    stringr::str_detect(dis, "[123456]"), 1, 0, missing = 0),
                NCR8_num = dplyr::if_else((dop + 30) <= dmort30 |
                                          dis == "6", 1, 0, missing = 0))

#Patients without contraindication discharged on lipid-lowering therapy
pci_data <- pci_data |>
  dplyr::mutate(NCR9_den = dplyr::if_else(stringr::str_detect(dis, "[12345]") &
                                          ((dstp == "0" | dstp == "1") |
                                          (doll == "0" | doll == "1")), 1, 0, missing = 0),
                NCR9_num = dplyr::if_else(NCR9_den == 1 &
                                          (dstp == "1" | doll == "1"), 1, 0, missing = 0))

#Patients referred to cardiac rehabilitation or other secondary prevention program
pci_data <- pci_data |>
  dplyr::mutate(NCR10_den = dplyr::if_else(stringr::str_detect(dis, "[12345]") &
                                           (crehab == "-1" | crehab == "1" | crehab == "0"), 1, 0, missing = 0),
                NCR10_num = dplyr::if_else(NCR10_den == 1 &
                                           crehab == "1", 1, 0, missing = 0))

#Proportion of patients without a clear and documented contraindication for aspirin and/or a P2Y12 inhibitor, discharged on DAPT
pci_data <- pci_data |>
  dplyr::mutate(NCR11_den = dplyr::if_else(stringr::str_detect(dis, "[12345]") &
                                           ((dasp == "0" | dasp == "1") |
                                           (doap == "0" | doap == "1")), 1, 0, missing = 0),
                NCR11_num = dplyr::if_else(NCR9_den == 1 &
                                           (dasp == "1" & doap == "1"), 1, 0, missing = 0))
```

\newpage

This report summarises the National Cardiac Registry Indicators for Percutaneous Coronary Intervention.

# Patterns in SPC Charts and Funnel Plots

The following patterns are highlighted in this report.

## Astronomical Point

An identified point that exceeds 3 sigma limits from the mean.

```{r showing astro sample, echo = FALSE}
spc_example_plotly(spc_example_data_astro)
```

## Trend

Five or more consecutively increasing or decreasing points.

```{r showing trend sample, echo = FALSE}
spc_example_plotly(spc_example_data_trend)
```

## Two in Three

Two out of Three consecutive points exceeding 2 sigma limits from the mean.

```{r showing two in three sample, echo = FALSE}
spc_example_plotly(spc_example_data_twothree)
```

## Shift

Seven or more consecutive points above or below the mean.

```{r showing shift sample, echo = FALSE}
spc_example_plotly(spc_example_data_shift)
```

## Funnel Plot Outlier

An identified point that exceeds 3 sigma limits from the mean.

```{r showing Funnel Outlier sample, echo = FALSE}
funnel_example_plotly(fpl_example_data)
```

# Patient Demographics

## All patients by Age and Sex

```{r Split Demographics, fig.width=8, fig.height=5}
# ggplot will be used for all plotting (aside from control charts)
library(ggplot2)
# The ggstats package provides several helpful utilities for plotting summarising data
library(ggstats)

pci_data |>
  ## 1 NA age record appears in the cohort, remove these values.
  dplyr::filter(!is.na(age) & sex_name %in% c("Female", "Male")) |>
  ggplot(aes(x = age_cat, fill = sex_name, by = 1, y = after_stat(prop))) +
    geom_prop_bar() +
    geom_prop_text() +
    theme_minimal() +
    scale_fill_manual(values = c("Female" = "#d62728", "Male" = "#0047AB", "Other" = "grey")) +
    scale_y_continuous(labels = scales::percent) +
    # Label axis and Title
    labs(
      title = "Proportion of all Patients by Age & Sex",
      x = "Age Category",
      y = "Proportion (%)",
      fill = "Sex"
    ) +
    theme(
      legend.position = "bottom"
    )

```

## All Aboriginal patients by Age and Sex

```{r Split Aboriginal Demographics, fig.width=8, fig.height=5}
pci_data |>
  ## 1 NA age record appears in the cohort, remove these values.
  dplyr::filter(!is.na(age) & sex_name %in% c("Female", "Male") & inds_name == "Aboriginal") |>
  ggplot(aes(x = age_cat, fill = sex_name, by = 1, y = after_stat(prop))) +
    geom_prop_bar() +
    geom_prop_text() +
    theme_minimal() +
    scale_fill_manual(values = c("Female" = "#d62728", "Male" = "#0047AB", "Other" = "grey")) +
    scale_y_continuous(labels = scales::percent) +
    # Label axis and Title
    labs(
      title = "Proportion of ATSI Patients by Age and Sex",
      x = "Age Category",
      y = "Proportion ATSI (%)",
      fill = "Sex"
    ) +
    theme(
      legend.position = "bottom"
    )
```

# Time from diagnostic ECG to PCI mediated reperfusion

## SPC

```{r NCR1 SPC}
## Generate the SPC chart
NCR1_spc <- controlcharts::spc(data = dplyr::filter(pci_data, NCR1_den == 1),
                   keys = period_end,
                   numerators = ecgdb,
                   aggregations = list(numerators = "median"),
                   spc_settings = list(chart_type = "i"),
                   y_axis_settings = list(ylimit_label = "Median time from ECG to PCI (Minutes)",
                                          ylimit_sig_figs = 0,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR1_spc
```

# Time from door to PCI mediated reperfusion

## SPC

```{r NCR2 SPC}
## Generate the SPC chart
NCR2_spc <- controlcharts::spc(data = dplyr::filter(pci_data, NCR2_den == 1),
                   keys = period_end,
                   numerators = dbdt,
                   aggregations = list(numerators = "median"),
                   spc_settings = list(chart_type = "i"),
                   y_axis_settings = list(ylimit_label = "Median time from door to PCI (Minutes)",
                                          ylimit_sig_figs = 0,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR2_spc
```

# Peri-PCI stroke

## Funnel

```{r NCR3 Funnel}
## Generate the Funnel chart
NCR3_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = ihstr,
                      denominators = NCR3_den,
                      y_axis_settings = list(ylimit_u = 2,
                                             ylimit_label = "% in-hospital stroke after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR3_fpl$static_plot
```

The funnel plot above displays the information for **Peri-PCI Stroke** between **`r min(pci_data$period_start)`** and **`r max(pci_data$period_end)`**. The mean (or center line) value statewide is **`r round(NCR3_fpl$limits$target[1], 2)`**.

```{r NCR3 SPC}
## Generate the SPC chart
NCR3_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = ihstr,
                   denominators = NCR3_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "% in-hospital stroke after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR3_spc
```

The Statistical Process Control (SPC) chart above displays the information for **Peri-PCI Stroke** between **`r min(pci_data$period_start)`** and **`r max(pci_data$period_end)`**. There was a total numerator of **`r format(sum(NCR3_fpl$limits$numerator), scientific = F, big.mark = ",")`**. There was a total denominator of **`r format(sum(NCR3_fpl$limits$denominator), scientific = F, big.mark = ",")`**. The mean (or center line) value statewide is **`r round(NCR3_fpl$limits$target[1], 2)`**.

# In-Hospital Major Bleeding

## Funnel

```{r NCR4 Funnel}
## Generate the Funnel chart
NCR4_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR4_num,
                      denominators = NCR4_den,
                      y_axis_settings = list(ylimit_u = 2,
                                             ylimit_label = "% in-hospital major bleeding after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR4_fpl
```

## SPC

```{r NCR4 SPC}
## Generate the SPC chart
NCR4_spc <- controlcharts::spc(data = dplyr::filter(pci_data, NCR4_den > 0),
                   keys = period_end,
                   numerators = NCR4_num,
                   denominators = NCR4_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "% in-hospital major bleeding after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR4_spc
```

# In-hospital mortality

## Funnel

```{r NCR5 Funnel}
## Generate the Funnel chart
NCR5_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR5_num,
                      denominators = NCR5_den,
                      y_axis_settings = list(ylimit_u = 5,
                                             ylimit_label = "% in-hospital mortality after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR5_fpl
```

## SPC

```{r NCR5 SPC}
## Generate the SPC chart
NCR5_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR5_num,
                   denominators = NCR5_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "% in-hospital mortality after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR5_spc
```

# 30 day unplanned cardiac readmission rate after PCI

Cardiac readmission data is currently undergoing review. This data was not included in the 2024 NCR data submission.

## Funnel

```{r NCR6 Funnel}
## Generate the Funnel chart
NCR6_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR6_num,
                      denominators = NCR6_den,
                      y_axis_settings = list(ylimit_u = 10,
                                             ylimit_label = "% 30 day unplanned cardiac readmissions after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR6_fpl
```

## SPC

```{r NCR6 SPC}
## Generate the SPC chart
NCR6_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR6_num,
                   denominators = NCR6_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "% 30 day unplanned cardiac readmissions after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR6_spc
```

# 30 day unplanned revascularisation rate after PCI

## Funnel

```{r NCR7 Funnel}
## Generate the Funnel chart
NCR7_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR7_num,
                      denominators = NCR7_den,
                      y_axis_settings = list(ylimit_label = "% 30 day unplanned revascularisation after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR7_fpl
```

## SPC

```{r NCR7 SPC}
## Generate the SPC chart
NCR7_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR7_num,
                   denominators = NCR7_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "% 30 day unplanned revascularisation after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR7_spc
```

# 30 Day Mortality

## Funnel

```{r NCR8 Funnel}
## Generate the Funnel chart
NCR8_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR8_num,
                      denominators = NCR8_den,
                      y_axis_settings = list(ylimit_u = 5,
                                             ylimit_label = "% 30 day mortality after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "decrease",
                                              three_sigma = TRUE))
NCR8_fpl
```

## SPC

```{r NCR8 SPC}
## Generate the SPC chart
NCR8_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR8_num,
                   denominators = NCR8_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "% 30 day mortality after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "decrease",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR8_spc
```

# Patients Referred to Cardiac Rehabilitation

## Funnel

```{r NCR10 Funnel}
## Generate the Funnel chart
NCR10_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR10_num,
                      denominators = NCR10_den,
                      y_axis_settings = list(ylimit_l = 70,
                                             ylimit_label = "% patients referred to cardiac rehab after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "increase",
                                              three_sigma = TRUE))
NCR10_fpl
```

## SPC

```{r NCR10 SPC}
## Generate the SPC chart
NCR10_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR10_num,
                   denominators = NCR10_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "% patients referred to cardiac rehab after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "increase",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR10_spc
```

# Patients Discharged on Lipid-Lowering Therapy

## Funnel

```{r NCR9 Funnel}
## Generate the Funnel chart
NCR9_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR9_num,
                      denominators = NCR9_den,
                      y_axis_settings = list(ylimit_u = 100,
                                             ylimit_l = 95,
                                             ylimit_label = "% patients discharged on Lipid Lowering Therapy after PCI",
                                             ylimit_sig_figs = 1,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "increase",
                                              three_sigma = TRUE))
NCR9_fpl
```

## SPC

There is an explained error in the discharge medication data for October 2021, this point can be ignored for analysis.

```{r NCR9 SPC}
## Generate the SPC chart
NCR9_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR9_num,
                   denominators = NCR9_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "% patients discharged on Lipid Lowering Therapy after PCI",
                                          ylimit_sig_figs = 1,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "increase",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR9_spc
```

# Patients Discharged on Dual Antiplatelet Therapy

## Funnel

```{r NCR11 Funnel}
## Generate the Funnel chart
NCR11_fpl <- controlcharts::funnel(data = pci_data,
                      keys = hname,
                      numerators = NCR11_num,
                      denominators = NCR11_den,
                      y_axis_settings = list(ylimit_u = 100,
                                             ylimit_l = 95,
                                             ylimit_label = "% patients discharged on Dual Antiplatelet Therapy after PCI",
                                             ylimit_sig_figs = 0,
                                             ylimit_label_size = 14),
                      x_axis_settings = list(xlimit_label = "Number of PCI's",
                                             xlimit_label_size = 14),
                      outlier_settings = list(improvement_direction = "increase",
                                              three_sigma = TRUE))
NCR11_fpl
```

## SPC

There is an explained error in the discharge medication data for October 2021, this point can be ignored for analysis.

```{r NCR11 SPC}
## Generate the SPC chart
NCR11_spc <- controlcharts::spc(data = pci_data,
                   keys = period_end,
                   numerators = NCR11_num,
                   denominators = NCR11_den,
                   spc_settings = list(chart_type = "p"),
                   y_axis_settings = list(ylimit_label = "% patients discharged on Dual Antiplatelet Therapy after PCI",
                                          ylimit_sig_figs = 0,
                                          ylimit_label_size = 14),
                   outlier_settings = list(improvement_direction = "increase",
                                           astronomical = TRUE,
                                           shift = TRUE,
                                           trend = TRUE,
                                           two_in_three = TRUE),
                   canvas_settings = list(upper_padding = 40),
                   nhs_icon_settings = list(show_variation_icons = TRUE),
                   date_settings = list(date_format_day = "(blank)",
                                    date_format_month = "Mon",
                                    date_format_year = "YY"))
NCR11_spc
```
