---
title: "`r {
  capitalise <- function(x) {
    paste0(toupper(substr(x, 1, 1)), tolower(substr(x, 2, nchar(x))))
  }
  title <- paste0('PCI Report - ', capitalise(Sys.getenv('QUARTO_PROFILE')))
  if (!is.na(params$target_id)) {
    title <- paste(title, params$target_id)
  }
  title
}`"
format:
  docx:
    toc: true
    number-sections: true
    highlight-style: github
    fig-format: svg
  html:
    toc: true
    toc-location: left
    embed-resources: true
params:
  target_id: !expr NA
knitr:
  opts_chunk:
    dev: "svglite"
execute:
  echo: false
---
```{r, include=FALSE}
gtsummary::theme_gtsummary_printer(print_engine = "flextable")
```

```{r Data download, include=FALSE}
if (!file.exists("./pci_data.csv")) {
  stop("NCR dataset not found! Please check that you have a single CSV file named 'pci_data.csv' in the current directory!",
       call. = FALSE)
}

#Load in the helper functions/data required
source("HelperFunctions.R")

#Read in data from PowerBI
pci_data <- readr::read_csv("./pci_data.csv", col_types = colTypes)
```

```{r Report context setup, include=FALSE}
# Report context setup - controls statewide/hospital/clinician mode
report_context <- Sys.getenv("QUARTO_PROFILE")
target_id <- params$target_id

# Validate parameters
if (report_context %in% c("hospital", "clinician") && is.na(target_id)) {
  stop("target_id must be provided for hospital or clinician context", call. = FALSE)
}
```

```{r Data transformation, include=FALSE}
pci_data <- prepare_pci_data(pci_data)
```

\newpage

This report summarises the National Cardiac Registry Indicators for Percutaneous Coronary Intervention.

::: {.callout-tip collapse="true"}
# Patterns in SPC Charts and Funnel Plots

The following patterns are highlighted in this report.

## Astronomical Point

An identified point that exceeds 3 sigma limits from the mean.

```{r showing astro sample, echo = FALSE}
spc_example_plotly(spc_example_data_astro)
```

## Trend

Five or more consecutively increasing or decreasing points.

```{r showing trend sample, echo = FALSE}
spc_example_plotly(spc_example_data_trend)
```

## Two in Three

Two out of Three consecutive points exceeding 2 sigma limits from the mean.

```{r showing two in three sample, echo = FALSE}
spc_example_plotly(spc_example_data_twothree)
```

## Shift

Seven or more consecutive points above or below the mean.

```{r showing shift sample, echo = FALSE}
spc_example_plotly(spc_example_data_shift)
```

## Funnel Plot Outlier

An identified point that exceeds 3 sigma limits from the mean.

```{r showing Funnel Outlier sample, echo = FALSE}
funnel_example_plotly(fpl_example_data)
```

:::

# Patient Demographics

## Patient Characteristics by Clinical Presentation

```{r demographics by acs, message=FALSE, warning=FALSE}
# Adding and formatting columns for use in demographics tables
table_data <- get_table_data(pci_data) |>
  dplyr::filter(!is.na(age) & !is.na(inds_cat) & !is.na(acs_cat))

# Statewide: columns are clinical presentation
# Hospital/Clinician: within each clinical presentation, compare Target vs Other
if (report_context == "statewide") {
  table_data |>
    gtsummary::tbl_summary(
      include = c(age, sex_cat, inds_cat, bmi, severe_obesity, los_cat, db, pvd, ppci, pcabg, shock, oca),
      by = "acs_cat",
      label = list(
        age ~ "Age",
        sex_cat ~ "Sex",
        inds_cat ~ "Indigenous Status",
        db ~ "Diabetic",
        pvd ~ "Peripheral Vascular Disease",
        bmi ~ "BMI",
        severe_obesity ~ "Severe Obesity (BMI ≥ 35 kg/m²)",
        ppci ~ "Previous PCI",
        pcabg ~ "Previous CABG",
        shock ~ "Cardiogenic Shock",
        oca ~ "Out of Hospital Cardiac Arrest",
        los_cat ~ "Length of Stay"
      ),
      statistic = list(
        c(age, bmi) ~ "{mean} ({sd})",
        c(sex_cat, inds_cat, db, pvd, severe_obesity, ppci, pcabg, shock, oca, los_cat) ~ "{n} ({p}%)"
      ),
      digits = list(
        c(age, bmi) ~ 1
      ),
      missing = "no"
    )
} else {
  table_data |>
    gtsummary::tbl_strata(
      strata = "acs_cat",
      .tbl_fun = ~ gtsummary::tbl_summary(
        .x,
        include = c(age, sex_cat, inds_cat, bmi, severe_obesity, los_cat, db, pvd, ppci, pcabg, shock, oca),
        by = "comparison_group",
        label = list(
          age ~ "Age",
          sex_cat ~ "Sex",
          inds_cat ~ "Indigenous Status",
          db ~ "Diabetic",
          pvd ~ "Peripheral Vascular Disease",
          bmi ~ "BMI",
          severe_obesity ~ "Severe Obesity (BMI ≥ 35 kg/m²)",
          ppci ~ "Previous PCI",
          pcabg ~ "Previous CABG",
          shock ~ "Cardiogenic Shock",
          oca ~ "Out of Hospital Cardiac Arrest",
          los_cat ~ "Length of Stay"
        ),
        statistic = list(
          c(age, bmi) ~ "{mean} ({sd})",
          c(sex_cat, inds_cat, db, pvd, severe_obesity, ppci, pcabg, shock, oca, los_cat) ~ "{n} ({p}%)"
        ),
        digits = list(
          c(age, bmi) ~ 1
        ),
        missing = "no"
      )
    )
}
```

## All patients by Age and Sex

```{r Split Demographics, fig.width=8, fig.height=5}
# ggplot will be used for all plotting (aside from control charts)
library(ggplot2)
# The ggstats package provides several helpful utilities for plotting summarising data
library(ggstats)

age_plt <- pci_data |>
  ## 1 NA age record appears in the cohort, remove these values.
  dplyr::filter(!is.na(age_cat)) |>
  ggplot(aes(x = age_cat, fill = sex_cat, by = 1, y = after_stat(prop))) +
    geom_prop_bar() +
    geom_prop_text() +
    theme_minimal() +
    scale_fill_manual(values = c("Female" = "#d62728", "Male" = "#0047AB", "Other" = "grey")) +
    scale_y_continuous(labels = scales::percent) +
    # Label axis and Title
    labs(
      title = "Proportion of all Patients by Age & Sex",
      x = "Age Category",
      y = "Proportion (%)",
      fill = "Sex"
    ) +
    theme(
      legend.position = "bottom"
    )

print_ggplot(age_plt)
```

# Clinical Characteristics

## Proportion of Patients with Previous PCI

```{r fpl_setup_ppci}
#| fig.cap="Funnel plot for the proportion of patients with a previous PCI"
fpl_data <- pci_funnel(
  data = pci_data,
  numerator_col = "ppci",
  y_axis_settings = list(
    ylimit_label = "% PCI Patients with a previous PCI",
    ylimit_label_size = 14,
    ylimit_sig_figs = 1,
    ylimit_u = 35
  ),
  outlier_settings = list(improvement_direction = "decrease", three_sigma = TRUE)
)
fpl_data
```

```{r spc_setup_ppci}
#| fig.cap="SPC chart for the proportion of patients with a previous PCI"
spc_data <- pci_spc(
  data = pci_data,
  numerator_col = "ppci",
  y_axis_settings = list(
    ylimit_label = "% PCI Patients with a previous PCI",
    ylimit_label_size = 14,
    ylimit_tick_rotation = 0,
    ylimit_sig_figs = 0
  ),
  outlier_settings = list(improvement_direction = "decrease")
)
spc_data
```

## Proportion of Patients with a previous CABG

```{r fpl_setup_pcabg}
#| fig.cap="Funnel plot for the proportion of patients with a previous CABG"
fpl_data <- pci_funnel(
  data = pci_data,
  numerator_col = "pcabg",
  y_axis_settings = list(
    ylimit_label = "% PCI Patients with a previous CABG",
    ylimit_label_size = 14,
    ylimit_sig_figs = 1,
    ylimit_u = 7
  ),
  outlier_settings = list(improvement_direction = "decrease", three_sigma = TRUE)
)
fpl_data
```

```{r spc_setup_pcabg}
#| fig.cap="SPC chart for the proportion of patients with a previous CABG"
spc_data <- pci_spc(
  data = pci_data,
  numerator_col = "pcabg",
  y_axis_settings = list(
    ylimit_label = "% PCI Patients with a previous CABG",
    ylimit_label_size = 14,
    ylimit_tick_rotation = 0,
    ylimit_sig_figs = 0
  ),
  outlier_settings = list(improvement_direction = "decrease")
)
spc_data
```

# Procedural Characteristics

This section presents procedural characteristics stratified by key patient and hospital factors, following the NCR Annual Report structure.

## Procedural Characteristics by Clinical Presentation

```{r procedural by acs, message=FALSE, warning=FALSE}
table_data <- get_table_data(pci_data) |>
  dplyr::filter(!is.na(acs_cat))

if (report_context == "statewide") {
  table_data |>
    gtsummary::tbl_summary(
      include = c(access_route, radial_access, des_used, any_isr, multi_vessel, num_lesions),
      by = "acs_cat",
      label = list(
        access_route ~ "Arterial Access Route",
        radial_access ~ "Radial Access",
        des_used ~ "Drug-Eluting Stent Used",
        any_isr ~ "In-Stent Restenosis",
        multi_vessel ~ "Multi-Vessel Disease",
        num_lesions ~ "Number of Lesions"
      ),
      type = list(
        num_lesions ~ "continuous"
      ),
      statistic = list(
        c(access_route, radial_access, des_used, any_isr, multi_vessel) ~ "{n} ({p}%)",
        c(num_lesions) ~ "{mean} ({sd})"
      ),
      digits = list(
        c(num_lesions) ~ 1
      ),
      missing = "no"
    ) |>
    add_overall_if_statewide(report_context = report_context)
} else {
  table_data |>
    gtsummary::tbl_strata(
      strata = "acs_cat",
      .tbl_fun = ~ gtsummary::tbl_summary(
        .x,
        include = c(access_route, radial_access, des_used, any_isr, multi_vessel, num_lesions),
        by = "comparison_group",
        label = list(
          access_route ~ "Arterial Access Route",
          radial_access ~ "Radial Access",
          des_used ~ "Drug-Eluting Stent Used",
          any_isr ~ "In-Stent Restenosis",
          multi_vessel ~ "Multi-Vessel Disease",
          num_lesions ~ "Number of Lesions"
        ),
        type = list(
          num_lesions ~ "continuous"
        ),
        statistic = list(
          c(access_route, radial_access, des_used, any_isr, multi_vessel) ~ "{n} ({p}%)",
          c(num_lesions) ~ "{mean} ({sd})"
        ),
        digits = list(
          c(num_lesions) ~ 1
        ),
        missing = "no"
      ) |>
        add_overall_if_statewide(report_context = report_context)
    )
}
```
