---
title: "<span style='color:#0047AB; font-family:Arial;'>Western Australian Percutaneous Coronary Intervention Database Report</span>"
format:
  docx:
    toc: true
    number-sections: true
    highlight-style: github
    fig-format: svg
execute:
  echo: false
---

```{r data import, include=FALSE}
#Load in the helper functions/data required
source("HelperFunctions.R")

# PowerBI Token
tk <- qiverse.azure::get_az_tk('pbi_df')
# Load data from PowerBI
pci_data <- qiverse.powerbi::download_dataflow_table(workspace_name = "PCI Data Set",
                                                dataflow_name = "Redcap PCI Registry",
                                                table_name = "PCIRegistryData",
                                                access_token = tk$credentials$access_token, verbose = TRUE)
```

```{r Data transformation, include=FALSE}
#Create period start and end, first and last date of the month
pci_data <- pci_data |>
  dplyr::mutate(dop = as.Date(dop_top),
  period_start = lubridate::floor_date(dop, unit = "month"),
  period_end = lubridate::ceiling_date(period_start, unit = "month")-1,
#Create numerator columns
  prev_cabg_num = dplyr::if_else(pcabg == "Yes", 1, 0),
  prev_pci_num = dplyr::if_else(ppci == "Yes", 1, 0),
  prev_oca_num = dplyr::if_else(arrest_pre_pci == "Yes", 1, 0),
  dis_length = dplyr::case_when(
    dod == dop ~ "SDD",
    (dod-dop) >= 2 ~ ">1 day",
    (dod-dop) >= 1 ~ "1 day",
    .default = "Unknown")) |>
#Missing data filters
  dplyr::filter(!is.na(period_end)) |>
  dplyr::filter(period_end <= Sys.Date())

```

\newpage

## Demographics
```{r demographics_intro, echo=FALSE}
ggplot2::ggplot(pci_data, ggplot2::aes(x = centre)) +
  ggplot2::geom_bar(fill = "steelblue") +
  ggplot2::labs(title = "Distribution of PCI Procedures by Hospital",
       x = "Hospital",
       y = "Count") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10, face = "bold"))
```

```{r cumulative sum cases, echo=FALSE} 
# Group data to get cumulative counts for each centre over time
group_data <- pci_data |>
  dplyr::group_by(centre, period_end) |>
  dplyr::summarise(count = dplyr::n()) |>
  dplyr::arrange(centre, period_end) |>
  dplyr::group_by(centre) |>
  dplyr::mutate(cumulative_count = cumsum(count))

# Cumulative sum of PCI cases over time
ggplot2::ggplot(pci_data, ggplot2::aes(x = dop, colour = "Cumulative Total")) +
  ggplot2::stat_ecdf(ggplot2::aes(y = ggplot2::after_stat(y) * nrow(pci_data)), geom = "line", color = "black") +
  ggplot2::geom_col(data = group_data, mapping = ggplot2::aes(x = period_end, y = cumulative_count, fill = centre), position = "dodge", linewidth = 0) +
  ggplot2::labs(title = "Cumulative Total of PCI Cases Over Time",
       x = "Date of Procedure",
       y = "Cumulative Total of PCI Cases",
       fill = "Hospital",
       colour = "") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10, face = "bold")) +
  ggplot2::scale_y_continuous(breaks = scales::breaks_pretty(10))
```

```{r demographics_sex, echo=FALSE}
# Plotting the distribution of patients by sex
ggplot2::ggplot(pci_data, ggplot2::aes(x = sex) +
  ggplot2::geom_bar(fill = "steelblue") +
  ggplot2::labs(title = "Distribution of PCI Patients by Sex",
       x = "Sex",
       y = "Count") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10, face = "bold"))

```

```{r demographics_inds, echo=FALSE}
# Plotting the distribution of patients by Indigenous status
ggplot2::ggplot(pci_data, ggplot2::aes(x = inds)) +
  ggplot2::geom_bar(fill = "steelblue") +
  ggplot2::labs(title = "Distribution of PCI Patients by Aboriginal or Torres Strait Islander Identity",
       x = "Aboriginal or Torres Strait Islander Identity",
       y = "Count") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10, face = "bold"))

```

```{r demographics_age, echo=FALSE}
# Plotting the distribution of patients by age
ggplot2::ggplot(pci_data, ggplot2::aes(x = age)) +
  ggplot2::geom_bar(fill = "steelblue") +
  ggplot2::labs(title = "Distribution of PCI Patients by Age",
       x = "Age",
       y = "Count") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10, face = "bold"))
```

```{r procedures, echo=FALSE}
# Plotting the distribution of patients by ACS Type
ggplot2::ggplot(pci_data, ggplot2::aes(x = reorder(stringr::str_wrap(type_acs, 10), type_acs, FUN = length, decreasing = T))) +
  ggplot2::geom_bar(fill = "steelblue") +
  ggplot2::labs(title = "Distribution of PCI Patients by ACS Type",
       x = "ACS Type",
       y = "Count") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10, face = "bold"))

```

```{r pci_indication, echo=FALSE}
# Plotting the distribution of patients by PCI indication
ggplot2::ggplot(pci_data, ggplot2::aes(x = reorder(stringr::str_wrap(pci_indication_list, 10), pci_indication_list, FUN = length, decreasing = T)))+
  ggplot2::geom_bar(fill = "steelblue") +
  ggplot2::labs(title = "Distribution of PCI Patients by PCI Indication",
       x = "PCI Indication",
       y = "Count") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10, face = "bold"))

```

```{r same_day_discharge, echo=FALSE}
# Plotting the distribution of patients by ACS Type
ggplot2::ggplot(pci_data, ggplot2::aes(x = dis_length)) +
  ggplot2::geom_bar(fill = "steelblue") +
  ggplot2::labs(title = "Distribution of PCI Patients by Same Day Discharge",
       x = "Same Day Discharge",
       y = "Count") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10, face = "bold"))

```

```{r access, echo=FALSE}
# Plotting the distribution of patients by Access
ggplot2::ggplot(pci_data, ggplot2::aes(x = reorder(access, access, FUN = length, decreasing = T))) +
  ggplot2::geom_bar(fill = "steelblue") +
  ggplot2::labs(title = "Distribution of PCI Patients by Access Site",
       x = "Access Site",
       y = "Count") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10, face = "bold"))

```

```{r adjunctive, echo=FALSE}
pci_data <- pci_data |> 
  dplyr::mutate(type_adjunct___1 = dplyr::if_else(type_adjunct___1 == "Checked", 1, 0))

# Plotting the distribution of patients by Adjunctive device
ggplot2::ggplot(pci_data, ggplot2::aes(x = type_adjunct___1)) +
  ggplot2::geom_bar(fill = "steelblue") +
  ggplot2::labs(title = "Distribution of PCI Patients by Adjunctive Device",
       x = "Adjunctve Device",
       y = "Count") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10, face = "bold"))

```

## Proportion of Patients with a previous PCI

### Funnel Plot
```{r fpl_setup_ppci, echo=FALSE, fig.width=6, fig.height=4}
#| fig.cap="Funnel plot for the proportion of patients with a previous PCI"
fpl_data <- controlcharts::funnel(
  data = pci_data,
  keys = centre,
  numerators = prev_pci_num,
  denominators = rep(1, nrow(pci_data)),
  y_axis_settings = list(ylimit_label = paste0("% PCI Patients with a previous PCI"),
    ylimit_label_size = 14, ylimit_sig_figs = 1, ylimit_u = 35),
  outlier_settings = list(improvement_direction = "decrease", three_sigma = TRUE))
fpl_data
```

``` {r fpl_patterns_ppci, echo=FALSE, fig.width=3, fig.height=2}
#Filter the spc limits data to get the latest patterns identified
astpoint <- fpl_data$limits |> dplyr::filter(three_sigma == "deterioration")

pattern_text <- "Using the Making Data Count approach, no patterns were identified in the Funnel Plot."
#Only include text if a pattern was identified
pattern_text <- if(length(astpoint$group) != 0) {
    pattern_text <- paste0("An astronomical point was identified for ", stringr::str_flatten(astpoint$group, collapse = ", "), ".")}

```

`r pattern_text`

### SPC Chart
```{r spc_setup_ppci, echo=FALSE} 
#| fig.cap="SPC chart for the proportion of patients with a previous PCI"
spc_data <- controlcharts::spc(
  data = pci_data,
  keys = period_end,
  numerators = prev_pci_num,
  denominators = rep(1, nrow(pci_data)),
  spc_settings = list(chart_type = "p"),
  y_axis_settings = list(ylimit_label = "% PCI Patients with a previous PCI", ylimit_label_size = 14, ylimit_tick_rotation = 0, ylimit_sig_figs = 0),
  outlier_settings = list(improvement_direction = "decrease", astronomical = TRUE, shift = TRUE, trend = TRUE, two_in_three = TRUE),
  nhs_icon_settings = list(show_variation_icons = TRUE),
  date_settings = list(date_format_day = "(blank)", date_format_month = "Mon", date_format_year = "YY")
)
spc_data
```

``` {r spc_patterns_ppci, echo=FALSE}
#Filter the spc limits data to get the latest patterns identified
astpoint <- spc_data$limits |> dplyr::filter(astpoint != "none")
#Filter to the last point in the ordered dates
astpoint <- astpoint$date[length(astpoint$date)]
trend <- spc_data$limits |> dplyr::filter(trend != "none")
trend <- trend$date[length(trend$date)]
shift <- spc_data$limits |> dplyr::filter(shift != "none")
shift <- shift$date[length(shift$date)]
two_in_three <- spc_data$limits |> dplyr::filter(two_in_three != "none")
two_in_three <- two_in_three$date[length(two_in_three$date)]

pattern_text <- "Using the Making Data Count approach, the following most recent patterns have been identified in the SPC chart: "
#Only include text if a pattern was identified
if(length(astpoint) == 1) {
  pattern_text <- stringr::str_flatten(c(pattern_text, paste0("An astronomical point was identified on ", astpoint, ". ")))}
if(length(trend) == 1) {
  pattern_text <- stringr::str_flatten(c(pattern_text, paste0("A trend was identified on ", trend, ". ")))}
if(length(shift) == 1) {
  pattern_text <- stringr::str_flatten(c(pattern_text, paste0("A shift was identified on ", shift, ". ")))}
if(length(two_in_three) == 1) {
   pattern_text <- stringr::str_flatten(c(pattern_text, paste0("A two in three was identified on ", two_in_three, ". ")))}

if(stringr::str_length(pattern_text) != 112) patttern_text <- "Using the Making Data Count approach, no patterns were identified in the SPC chart."

```

`r pattern_text`

\newpage

## Proportion of Patients with a previous CABG

### Funnel Plot
```{r fpl_setup_pcabg, echo=FALSE}
#| fig.cap="Funnel plot for the proportion of patients with a previous CABG"
fpl_data <- controlcharts::funnel(
  data = pci_data,
  keys = centre,
  numerators = prev_cabg_num,
  denominators = rep(1, nrow(pci_data)),
  y_axis_settings = list(ylimit_label = paste0("% PCI Patients with a previous CABG"), 
    ylimit_label_size = 14, ylimit_sig_figs = 1, ylimit_u = 7),
  outlier_settings = list(improvement_direction = "decrease", three_sigma = TRUE)
)
fpl_data
```

``` {r fpl_patterns_pcabg, echo=FALSE}
#Filter the spc limits data to get the latest patterns identified
astpoint <- fpl_data$limits |> dplyr::filter(three_sigma == "deterioration")

pattern_text <- "Using the Making Data Count approach, no patterns were identified in the Funnel Plot."
#Only include text if a pattern was identified
pattern_text <- if(length(astpoint$group) != 0) {
    pattern_text <- paste0("An astronomical point was identified for ", stringr::str_flatten(astpoint$group, collapse = ", "), ".")}

```

`r pattern_text`

### SPC Chart
```{r spc_setup_pcabg, echo=FALSE} 
#| fig.cap="SPC chart for the proportion of patients with a previous CABG"
spc_data <- controlcharts::spc(
  data = pci_data,
  keys = period_end,
  numerators = prev_cabg_num,
  denominators = rep(1, nrow(pci_data)),
  spc_settings = list(chart_type = "p"),
  y_axis_settings = list(ylimit_label = "% PCI Patients with a previous CABG", ylimit_label_size = 14, ylimit_tick_rotation = 0, ylimit_sig_figs = 0),
  outlier_settings = list(improvement_direction = "decrease", astronomical = TRUE, shift = TRUE, trend = TRUE, two_in_three = TRUE),
  nhs_icon_settings = list(show_variation_icons = TRUE),
  date_settings = list(date_format_day = "(blank)", date_format_month = "Mon", date_format_year = "YY")
)
spc_data
```

``` {r spc_patterns_pcabg, echo=FALSE}
#Filter the spc limits data to get the latest patterns identified
astpoint <- spc_data$limits |> dplyr::filter(astpoint != "none")
#Filter to the last point in the ordered dates
astpoint <- astpoint$date[length(astpoint$date)]
trend <- spc_data$limits |> dplyr::filter(trend != "none")
trend <- trend$date[length(trend$date)]
shift <- spc_data$limits |> dplyr::filter(shift != "none")
shift <- shift$date[length(shift$date)]
two_in_three <- spc_data$limits |> dplyr::filter(two_in_three != "none")
two_in_three <- two_in_three$date[length(two_in_three$date)]

pattern_text <- "Using the Making Data Count approach, the following most recent patterns have been identified in the SPC chart: "
#Only include text if a pattern was identified
if(length(astpoint) == 1) {
  pattern_text <- stringr::str_flatten(c(pattern_text, paste0("An astronomical point was identified on ", astpoint, ". ")))}
if(length(trend) == 1) {
  pattern_text <- stringr::str_flatten(c(pattern_text, paste0("A trend was identified on ", trend, ". ")))}
if(length(shift) == 1) {
  pattern_text <- stringr::str_flatten(c(pattern_text, paste0("A shift was identified on ", shift, ". ")))}
if(length(two_in_three) == 1) {
   pattern_text <- stringr::str_flatten(c(pattern_text, paste0("A two in three was identified on ", two_in_three, ". ")))}

if(stringr::str_length(pattern_text) != 112) patttern_text <- "Using the Making Data Count approach, no patterns were identified in the SPC chart."
```

`r pattern_text`

\newpage

## Proportion of Patients with a previous OHCA

### Funnel Plot
```{r fpl_setup_pOHCA, echo=FALSE}
#| fig.cap="Funnel plot for the proportion of patients with a previous OHCA"
fpl_data <- controlcharts::funnel(
  data = pci_data,
  keys = centre,
  numerators = prev_oca_num,
  denominators = rep(1, nrow(pci_data)),
  y_axis_settings = list(ylimit_label = paste0("% PCI Patients with a previous OHCA"), 
    ylimit_label_size = 14, ylimit_sig_figs = 1, ylimit_u = 7),
  outlier_settings = list(improvement_direction = "decrease", three_sigma = TRUE)
)
fpl_data
```

``` {r fpl_patterns_pOHCA, echo=FALSE}
#Filter the spc limits data to get the latest patterns identified
astpoint <- fpl_data$limits |> dplyr::filter(three_sigma == "deterioration")

pattern_text <- "Using the Making Data Count approach, no patterns were identified in the Funnel Plot."
#Only include text if a pattern was identified
pattern_text <- if(length(astpoint$group) != 0) {
    pattern_text <- paste0("An astronomical point was identified for ", stringr::str_flatten(astpoint$group, collapse = ", "), ".")}

```

`r pattern_text`

### SPC Chart
```{r spc_setup_pOHCA, echo=FALSE} 
#| fig.cap="SPC chart for the proportion of patients with a previous OHCA"
spc_data <- controlcharts::spc(
  data = pci_data,
  keys = period_end,
  numerators = prev_oca_num,
  denominators = rep(1, nrow(pci_data)),
  spc_settings = list(chart_type = "p"),
  y_axis_settings = list(ylimit_label = "% PCI Patients with a previous OHCA", ylimit_label_size = 14, ylimit_tick_rotation = 0, ylimit_sig_figs = 0),
  outlier_settings = list(improvement_direction = "decrease", astronomical = TRUE, shift = TRUE, trend = TRUE, two_in_three = TRUE),
  nhs_icon_settings = list(show_variation_icons = TRUE),
  date_settings = list(date_format_day = "(blank)", date_format_month = "Mon", date_format_year = "YY")
)
spc_data
```

``` {r spc_patterns_pOHCA, echo=FALSE}
#Filter the spc limits data to get the latest patterns identified
astpoint <- spc_data$limits |> dplyr::filter(astpoint != "none")
#Filter to the last point in the ordered dates
astpoint <- astpoint$date[length(astpoint$date)]
trend <- spc_data$limits |> dplyr::filter(trend != "none")
trend <- trend$date[length(trend$date)]
shift <- spc_data$limits |> dplyr::filter(shift != "none")
shift <- shift$date[length(shift$date)]
two_in_three <- spc_data$limits |> dplyr::filter(two_in_three != "none")
two_in_three <- two_in_three$date[length(two_in_three$date)]

pattern_text <- "Using the Making Data Count approach, the following most recent patterns have been identified in the SPC chart: "
#Only include text if a pattern was identified
if(length(astpoint) == 1) {
  pattern_text <- stringr::str_flatten(c(pattern_text, paste0("An astronomical point was identified on ", astpoint, ". ")))}
if(length(trend) == 1) {
  pattern_text <- stringr::str_flatten(c(pattern_text, paste0("A trend was identified on ", trend, ". ")))}
if(length(shift) == 1) {
  pattern_text <- stringr::str_flatten(c(pattern_text, paste0("A shift was identified on ", shift, ". ")))}
if(length(two_in_three) == 1) {
   pattern_text <- stringr::str_flatten(c(pattern_text, paste0("A two in three was identified on ", two_in_three, ". ")))}

if(stringr::str_length(pattern_text) != 112) patttern_text <- "Using the Making Data Count approach, no patterns were identified in the SPC chart."


```

`r pattern_text`

\newpage

## Co-morbidities Breakdown

```{r co-morbidities, echo=FALSE}
comorbs <- c("db", "dbm", "pvd2", "stroke", "dyslipidaemia", "smk", "heart_failure", "htn", "lung_disease","dial")

 gtsummary::tbl_summary(pci_data,
    include = dplyr::all_of(comorbs),
    label = list(
      db ~ "Diabetes",
      dbm ~ "Diabetes Type",
      pvd2 ~ "Peripheral Vascular Disease",
      stroke ~ "Stroke",
      dyslipidaemia ~ "Dyslipidaemia",
      smk ~ "Smoking Status",
      heart_failure ~ "Heart Failure",
      htn ~ "Hypertension",
      lung_disease ~ "Lung Disease",
      dial ~ "Renal Dialysis"
    ),
    statistic = list(
      dplyr::all_of(comorbs) ~ "N: {n} | D: {N} | %: {p}"
    ),
    missing = "no"
  ) |> gtsummary::as_flex_table()


```

## Device Timing KPI Summary Table
```{r device_times_setup, echo=FALSE}

#Convert to numeric
pci_data$pain_device_time_4 <- as.numeric(pci_data$pain_device_time_4)

device_label = list(
      "Door to Device:" = list(
        door_device_kpi ~ "Ambulance (KPI <90)",
        door_device_time_2 ~ "PCI Centre ED (KPI <90)",
        door_device_time_3 ~ "Non PCI Centre ED (KPI <120)",
        door_device_time_5 ~ "Rescue PCI"),
      "FMC to Device:" = list(
        fmc_device_time ~ "Ambulance",
        fmc_device_time_2 ~ "PCI Centre ED",
        fmc_device_time_3 ~ "Non PCI Centre ED"),
      "Pain to Device:" = list(
        pain_device_time ~ "Ambulance",
        pain_device_time_2 ~ "PCI Centre ED",
        pain_device_time_3 ~ "Non PCI Centre ED",
        pain_device_time_4 ~ "PCI Centre Ward",
        pain_device_time_5 ~ "Rescue PCI")
      )
device_cols <- list(
      "Door to Device:" = c(
        "door_device_kpi",
        "door_device_time_2",
        "door_device_time_3",
        "door_device_time_5"),
      "FMC to Device:" = c(
        "fmc_device_time",
        "fmc_device_time_2",
        "fmc_device_time_3"),
      "Pain to Device:" = c(
        "pain_device_time",
        "pain_device_time_2",
        "pain_device_time_3",
        "pain_device_time_4",
        "pain_device_time_5")
      )

door_to_device <- gtsummary::tbl_summary(pci_data,
    include = dplyr::all_of(device_cols[["Door to Device:"]]),
    label = device_label[["Door to Device:"]],
    statistic = list(
      dplyr::all_of(device_cols[["Door to Device:"]]) ~ "Median: {median} | Mean: {mean} | SD: {sd} | Count: {N_nonmiss}"
    ),
    missing = "no"
  )

FMC_to_device <- gtsummary::tbl_summary(pci_data,
    include = dplyr::all_of(device_cols[["FMC to Device:"]]),
    label = device_label[["FMC to Device:"]],
    statistic = list(
      dplyr::all_of(device_cols[["FMC to Device:"]]) ~ "Median: {median} | Mean: {mean} | SD: {sd} | Count: {N_nonmiss}"
    ),
    missing = "no"
  )

pain_to_device <- gtsummary::tbl_summary(pci_data,
    include = dplyr::all_of(device_cols[["Pain to Device:"]]),
    label = device_label[["Pain to Device:"]],
    statistic = list(
      dplyr::all_of(device_cols[["Pain to Device:"]]) ~ "Median: {median} | Mean: {mean} | SD: {sd} | Count: {N_nonmiss}"
    ),
    missing = "no"
  )

#stack the tables together
combined_table <- gtsummary::tbl_stack(list(door_to_device, FMC_to_device, pain_to_device), 
  group_header = c("Door to Device Time", "First Medical Contact to Device Time", "Pain Onset to Device Time")) |>
    gtsummary::modify_header(label = "**Device Timing Indicators**")

combined_table |> 
  gtsummary::as_flex_table() |>
  flextable::set_table_properties(layout = "autofit")
```
### Ambulance Prenotified Arrival at PCI Centre to Device Time
```{r spc_setup_timings_pain_device, echo=FALSE} 

#Ambulance Arrival to device time
spc_data <- controlcharts::spc(
  data = dplyr::filter(pci_data, !is.na(door_device_kpi)),
  keys = period_end,
  numerators = door_device_kpi,
  spc_settings = list(chart_type = "i"),
  aggregations = list(numerators = "mean"),
  y_axis_settings = list(ylimit_label = "Mean Time (minutes)", 
    ylimit_label_size = 14, ylimit_tick_rotation = 0, ylimit_sig_figs = 0),
  line_settings = list(show_alt_target = TRUE, alt_target = 90, colour_alt_target = "#00667B"),
  outlier_settings = list(improvement_direction = "decrease", astronomical = TRUE, shift = TRUE, trend = TRUE, two_in_three = TRUE),
  nhs_icon_settings = list(show_variation_icons = TRUE),
  date_settings = list(date_format_day = "(blank)", date_format_month = "Mon", date_format_year = "YY"))
spc_data
```

### PCI Centre ED Arrival to Device Time
```{r spc_setup_timing_FMC_device, echo=FALSE} 

#PCI Centre ED arrival to device time
spc_data <- controlcharts::spc(
  data = dplyr::filter(pci_data, !is.na(door_device_time_2)),
  keys = period_end,
  numerators = door_device_time_2,
  spc_settings = list(chart_type = "i"),
  aggregations = list(numerators = "mean"),
  y_axis_settings = list(ylimit_label = "Mean Time (minutes)", 
    ylimit_label_size = 14, ylimit_tick_rotation = 0, ylimit_sig_figs = 0),
  line_settings = list(show_alt_target = TRUE, alt_target = 90, colour_alt_target = "#00667B"),
  outlier_settings = list(improvement_direction = "decrease", astronomical = TRUE, shift = TRUE, trend = TRUE, two_in_three = TRUE),
  nhs_icon_settings = list(show_variation_icons = TRUE),
  date_settings = list(date_format_day = "(blank)", date_format_month = "Mon", date_format_year = "YY")
)
spc_data
```

### Non-PCI Centre Arrival to Device Time
```{r spc_setup_timing_Door_device, echo=FALSE} 

#Non PCI Centre Door to device time
spc_data <- controlcharts::spc(
  data = dplyr::filter(pci_data, !is.na(door_device_time_3)),
  keys = period_end,
  numerators = door_device_time_3,
  spc_settings = list(chart_type = "i"),
  aggregations = list(numerators = "mean"),
  y_axis_settings = list(ylimit_label = "Mean Time (minutes)",
   ylimit_label_size = 14, ylimit_tick_rotation = 0, ylimit_sig_figs = 0),
     line_settings = list(show_alt_target = TRUE, alt_target = 120, colour_alt_target = "#00667B"),
  outlier_settings = list(improvement_direction = "decrease", astronomical = TRUE, shift = TRUE, trend = TRUE, two_in_three = TRUE),
  nhs_icon_settings = list(show_variation_icons = TRUE),
  date_settings = list(date_format_day = "(blank)", date_format_month = "Mon", date_format_year = "YY")
)
spc_data
```




## Editing the Report
This report is created using Quarto and R to produce a Microsoft Word output, if you want to edit the report styling to fit your reporting requirements, right click any graph and select Convert to Shape, this will allow you to edit graphs as needed.