---
title: "<span style='color:#0047AB; font-family:Arial;'>Customised Percutaneous Coronary Interventions Report</span>"
format:
  docx:
    toc: true
    number-sections: true
    highlight-style: github
    fig-format: svg
execute:
  echo: false
---

```{r data import, include=FALSE}
if (!file.exists("./pci_data.csv")) {
  stop("NCR dataset not found! Please check that you have a single CSV file named 'pci_data.csv' in the current directory!",
       call. = FALSE)
}

#Load in the helper functions/data required
source("HelperFunctions.R")

#Read in data from PowerBI
pci_data <- readr::read_csv("./pci_data.csv", col_types = colTypes)
```

```{r Data transformation, include=FALSE}
# Load in packages if required
library(dplyr)
# library(lubridate)
# library(controlcharts)

#Creating period start and end, first and last date of the month
pci_data <- pci_data |>
  dplyr::mutate(period_start = lubridate::floor_date(dop, unit = "month"),
                period_end = lubridate::ceiling_date(period_start, unit = "month")-1)

# Calculate numerators and denominators for Previous CABG, Previous PCI, Previous Cardiac Arrest & STEMI events
pci_data <- pci_data |>
  dplyr::mutate(
    prev_cabg_num = if_else(pcabg == 1, 1, 0),
    prev_pci_num = if_else(ppci == 1, 1, 0),
    prev_oca_num = if_else(oca == 1, 1, 0),
    acs_cat = dplyr::case_when(
      acst == 0 ~ "Non-ACS",
      acst == 1 ~ "NSTEMI",
      acst == 2 ~ "NSTEMI",
      acst == 3 ~ "STEMI"
    ),
    acs_stemi_num = if_else(acs_cat == "STEMI", 1, 0)
  )
```

\newpage

# Indicators for Previous Procedures

## Proportion of Patients with Previous CABG

### SPC Chart: Proportion of Patients with Previous CABG

```{r previous-cabg-spc}
prev_cabg_spc <- controlcharts::spc(
  data = pci_data,
  keys = period_end,
  numerators = prev_cabg_num,
  denominators = rep(1, nrow(pci_data)),
  spc_settings = list(chart_type = "p"),
  y_axis_settings = list(ylimit_label = "% Patients with Previous CABG", ylimit_label_size = 14),
  outlier_settings = list(improvement_direction = "decrease", astronomical = TRUE, shift = TRUE, trend = TRUE, two_in_three = TRUE),
  canvas_settings = list(upper_padding = 40),
  nhs_icon_settings = list(show_variation_icons = TRUE),
  date_settings = list(date_format_day = "(blank)", date_format_month = "Mon", date_format_year = "YY")
)
prev_cabg_spc
```

### Funnel Chart: Proportion of Patients with Previous CABG

```{r previous-cabg-funnel}
prev_cabg_funnel <- controlcharts::funnel(
  data = pci_data,
  keys = hname,
  numerators = prev_cabg_num,
  denominators = rep(1, nrow(pci_data)),
  y_axis_settings = list(ylimit_label = "% Patients with Previous CABG", ylimit_label_size = 14),
  outlier_settings = list(improvement_direction = "decrease", three_sigma = TRUE)
)
prev_cabg_funnel
```

## Proportion of Patients with Previous PCI

### SPC Chart: Proportion of Patients with Previous PCI

```{r previous-pci-spc}
prev_pci_spc <- controlcharts::spc(
  data = pci_data,
  keys = period_end,
  numerators = prev_pci_num,
  denominators = rep(1, nrow(pci_data)),
  spc_settings = list(chart_type = "p"),
  y_axis_settings = list(ylimit_label = "% Patients with Previous PCI", ylimit_label_size = 14),
  outlier_settings = list(improvement_direction = "decrease", astronomical = TRUE, shift = TRUE, trend = TRUE, two_in_three = TRUE),
  canvas_settings = list(upper_padding = 40),
  nhs_icon_settings = list(show_variation_icons = TRUE),
  date_settings = list(date_format_day = "(blank)", date_format_month = "Mon", date_format_year = "YY")
)
prev_pci_spc
```

### Funnel Chart: Proportion of Patients with Previous PCI

```{r previous-pci-funnel}
prev_pci_funnel <- controlcharts::funnel(
  data = pci_data,
  keys = hname,
  numerators = prev_pci_num,
  denominators = rep(1, nrow(pci_data)),
  y_axis_settings = list(ylimit_label = "% Patients with Previous PCI", ylimit_label_size = 14),
  outlier_settings = list(improvement_direction = "decrease", three_sigma = TRUE)
)
prev_pci_funnel
```

## Proportion of Patients with Previous Cardiac Arrest

### SPC Chart: Proportion of Patients with Previous Cardiac Arrest

```{r previous-oca-spc}
prev_oca_spc <- controlcharts::spc(
  data = pci_data,
  keys = period_end,
  numerators = prev_oca_num,
  denominators = rep(1, nrow(pci_data)),
  spc_settings = list(chart_type = "p"),
  y_axis_settings = list(ylimit_label = "% Patients with Previous Cardiac Arrest", ylimit_label_size = 14),
  outlier_settings = list(improvement_direction = "decrease", astronomical = TRUE, shift = TRUE, trend = TRUE, two_in_three = TRUE),
  canvas_settings = list(upper_padding = 40),
  nhs_icon_settings = list(show_variation_icons = TRUE),
  date_settings = list(date_format_day = "(blank)", date_format_month = "Mon", date_format_year = "YY")
)
prev_oca_spc
```

### Funnel Chart: Proportion of Patients with Previous Cardiac Arrest

```{r previous-oca-funnel}
prev_oca_funnel <- controlcharts::funnel(
  data = pci_data,
  keys = hname,
  numerators = prev_oca_num,
  denominators = rep(1, nrow(pci_data)),
  y_axis_settings = list(ylimit_label = "% Patients with Previous Cardiac Arrest", ylimit_label_size = 14),
  outlier_settings = list(improvement_direction = "decrease", three_sigma = TRUE)
)
prev_oca_funnel
```

\newpage

## Indicators for Clinical Procedure

### SPC Chart: Proportion of STEMI Presentations

```{r stemi-spc}
stemi_spc <- controlcharts::spc(
  data = pci_data,
  keys = period_end,
  numerators = acs_stemi_num,
  denominators = rep(1, nrow(pci_data)),
  spc_settings = list(chart_type = "p"),
  y_axis_settings = list(ylimit_label = "% STEMI Presentations", ylimit_label_size = 14),
  outlier_settings = list(improvement_direction = "decrease", astronomical = TRUE, shift = TRUE, trend = TRUE, two_in_three = TRUE),
  canvas_settings = list(upper_padding = 40),
  nhs_icon_settings = list(show_variation_icons = TRUE),
  date_settings = list(date_format_day = "(blank)", date_format_month = "Mon", date_format_year = "YY")
)
stemi_spc
```

### Funnel Chart: Proportion of STEMI Presentations

```{r stemi-funnel}
stemi_funnel <- controlcharts::funnel(
  data = pci_data,
  keys = hname,
  numerators = acs_stemi_num,
  denominators = rep(1, nrow(pci_data)),
  y_axis_settings = list(ylimit_label = "% STEMI Presentations", ylimit_label_size = 14),
  outlier_settings = list(improvement_direction = "decrease", three_sigma = TRUE)
)
stemi_funnel
```



